Applying Computational Intelligence Methods for Predicting the Sales of Newly Published Books in a Real Editorial Business Management Environment

### 2016-09-07 paper.tex
clarifying some details in section-6
solving some TODOs

%********************************************************************************
\section{State of the art on sales forecasting} 
\label{sec:soa}
% Antonio - TODO: Since two new sections have been added here, maybe we should change the title of the section... Maybe 'Background and related works'?
% I don't see how or what the new title might change ....  ???   we can discuss this item later this morning.

@@

% Antonio - TODO: link this section with the rest of the SotA. Introduce it in a paragraph before.
Many of the previous papers propose using different prediction methods.
Thus, next subsections describe several forecasting methods and different 
evaluation criteria, commonly used in the bibliography that have been chosen 
to face the problem at hand.

%-------------------------------------------------
\subsection{Selecting an appropriate forecasting method}
\label{subsec:select_method}

@@

Thus, in this research five forecasting methods, based on the State of the Art 
literature review (see above, Section \ref{sec:soa}) 
\cite{Madsen2008,ChingChin2010,Thomassey2012,Xia2012,SThomassey2014}, 
have been used. 
Well known forecasting methods implemented in the Weka tool have been chosen, 
as these methods are widely known, and could be very helpful for practitioners 
to reproduce experiments and even to solve similar sales prediction problems 
using these methods.

@@

\begin{figure*}[ht]
\begin{center}
\includegraphics[scale=0.6]{./imgs/attribute_All.eps}
\end{center}
\caption{Boxplots showing the values obtained predicting \texttt{total\_sales} with different regression methods (30 repetitions, 10-fold cross validation). Results obtained for different special publishing companies: UDL929 (the best selling publishing company), UDLW12 (the median selling publishing company), UDL704 (highest number of different titles sold) and UDLU11 (medium number of different books sold). Just the features selected by ReliefFAttributeEval method have been considered.}
\label{fig:attributeAll}
\end{figure*}
% Antonio - CONCERN - The text and the results must be contrasted. If I'm not wrong, I remember that we decided to include here just the results obtained by ReliefFAttributeEval, since they were quite good (maybe the best). But there are plotted apparently the results for all the features. Anyway, in the text, it is said that the process is using all the features, then apply FS. But here just the results for all the features are shown. Why don't we show also the results for the corresponding sets of features selected by each FS method?
% Actually in the previous version there were several tables with these results than have been moved to the Appendix. I think we should include another figure fro them. They show important information. ;)
% we can discuss this point later this morning. If necessary, we can design and include a new plot.

@@

>>>>

%********************************************************************************
\section{Background and State of the art on sales forecasting} 
\label{sec:soa}

@@

Many of the previous papers propose using different prediction methods.
Thus, next subsections describe several forecasting methods and different 
evaluation metrics, commonly used in the bibliography that have been chosen 
to face the problem at hand.

%-------------------------------------------------
\subsection{Regression methods}
\label{subsec:select_method}

@@

Thus, in this research six forecasting methods, based on the State of the Art 
literature review (see above, Section \ref{sec:soa}) 
\cite{Madsen2008,ChingChin2010,Thomassey2012,Xia2012,SThomassey2014}, 
have been used. 
Well known forecasting methods implemented in the Weka tool have been chosen, 
as these methods are widely known, and could be very helpful for practitioners 
to reproduce experiments and even to solve similar sales prediction problems 
using these methods.

@@

\begin{figure*}[ht]
\begin{center}
\includegraphics[scale=0.6]{./imgs/attribute_All.eps}
\end{center}
\caption{Boxplots showing the values obtained predicting \texttt{total\_sales}, using all features, with different regression methods (30 repetitions, 10-fold cross validation). Results obtained for different special publishing companies: UDL929 (the best selling publishing company), UDLW12 (the median selling publishing company), UDL704 (highest number of different titles sold) and UDLU11 (medium number of different books sold).
% Just the features selected by ReliefFAttributeEval method have been considered.
}
\label{fig:attributeAll}
\end{figure*}
% Antonio - CONCERN - The text and the results must be contrasted. If I'm not wrong, I remember that we decided to include here just the results obtained by ReliefFAttributeEval, since they were quite good (maybe the best). But there are plotted apparently the results for all the features. Anyway, in the text, it is said that the process is using all the features, then apply FS. But here just the results for all the features are shown. Why don't we show also the results for the corresponding sets of features selected by each FS method?
% Actually in the previous version there were several tables with these results than have been moved to the Appendix. I think we should include another figure fro them. They show important information. ;)
% we can discuss this point later this morning.
% The thing is that in this plot we are using all features!! (here, no feature selection method has been used)

@@

% [pedro]  TODO => una vez hecha la nueva figura, volver a meter este comentario anterior (lin.1297)
